NumLin: Linear Types for Linear Algebra

### 2019-06-29 write-up/paper/implementation.tex
Update implementation.tex

\begin{figure}[tp]
    \centering
    \begin{minted}[fontsize=\small]{ocaml}
let rec f i n x0 row =
  if Prim.extract @@ Prim.eqI i n then (row, x0)
  else
    let row, x1 = Prim.get row i in
    f (Prim.addI i (Many 1)) n (Prim.addE x0 x1) row
in
f
    \end{minted}
    \caption{Recursive OCaml function for a summing over an array, generated (at
        \emph{compile time}) from the code in Figure~\ref{fig:lang_sumarray},
        passed through \texttt{ocamlformat} for presentation.}\label{fig:ocaml_sumarray}
\end{figure}

>>>>

\begin{figure}[tp]
    \centering
    \begin{minted}[fontsize=\small]{ocaml}
let rec sum_array i n x0 row =
  if Prim.extract @@ Prim.eqI i n then (row, x0)
  else
    let row, x1 = Prim.get row i in
    sum_array (Prim.addI i (Many 1)) n (Prim.addE x0 x1) row in
sum_array
    \end{minted}
    \caption{Recursive OCaml function for a summing over an array, generated (at
        \emph{compile time}) from the code in Figure~\ref{fig:lang_sumarray},
        passed through \texttt{ocamlformat} for presentation.}\label{fig:ocaml_sumarray}
\end{figure}
